---
title: "SERL pilot study paper analysis"
author: "Ellen Webborn"
date: 'Last run at: `r Sys.time()`'
output:
  word_document
---

```{r setup, include=FALSE}

library(data.table) 
library(ggplot2) 
library(broom) 
library(car) 
library(stringr)
library(flextable)
library(RColorBrewer)

# Set figure defaults
fig.h <- 5.5
fig.w <- 10
fullwidth <- TRUE
font.size <- 18
title.size <- 14
geom.text.size <- 7

knitr::opts_chunk$set(echo = FALSE, include = FALSE, message = FALSE, warning = FALSE, fig.width = fig.w, fig.height = fig.h, fig.fullwidth = fullwidth, dpi = 300)

options(scipen=999)

```


```{r functions}

# Format numbers with % in output tables
format.percents <-
  function(dt,
           perc_cols = c("ResponseRate", "LowerCI", "UpperCI"),
           decimals = 2) {
    for (j in perc_cols) {
      dt[, eval(j) := paste(format(round(get(j), digits = decimals), nsmall = decimals),
                            "%", sep = "")]
    }
    dt
  }

# Format output tables
my.flex <- function(t, autofit = FALSE) {
  ft <- flextable(t)
  ft <- theme_booktabs(ft)
  ft <- theme_zebra(ft, 
                    odd_header = rgb(84/255, 141/255, 212/255, 1),
                    even_body = "transparent",
                    odd_body = rgb(242/255, 242/255, 242/255, 1))
  ft <- color(ft, color = "white", part = "header")
  ft <- italic(ft, italic = TRUE, part = "header")
  ft <- bold(ft, bold = FALSE, part = "header")
  if(autofit == TRUE) {
    ft <- autofit(ft)
  } else{
    ft <- set_table_properties(ft, layout = "autofit")
  }
  return(ft)
}

```

```{r import}

# load data
load("N:/Documents/My publications/Pilot study paper/pilot_response_data_final.RData")

# import font
windowsFonts(`LM Roman 10` = windowsFont("LM Roman 10"))
myFont <- "LM Roman 10"

```

```{r basicStats}

n_signups <- results[consent == TRUE, .N]
perc_signed_up <- round(n_signups / 18000 * 100, 1)
n_survey_started <- results[survey_status %in% c("Completed", "Partially completed"), .N]
perc_survey_started <- round(n_survey_started / n_signups * 100, 1)
perc_survey_completed <- round(results[survey_status %in% c("Completed"), .N] / 
                                 n_signups * 100, 1)

n_survey_online <- results[survey_response_type == "online", .N]
n_survey_post <- results[survey_response_type == "postal", .N]
n_survey_both <- results[survey_response_type == "online + postal", .N]

# Results with confidence intervals
respRate <- binom.test(
  results[consent == TRUE, .N],
  18000,
  p = n_signups/18000,
  alternative = "two.sided",
  conf.level = 0.95
)
signup_CI_low <- round(respRate$conf.int[1] * 100, 1)
signup_CI_high <- round(respRate$conf.int[2] * 100, 1)


```



# Abstract

Up to 4 mailings were sent to 18,000 addresses, recruiting `r n_signups` participants (`r perc_signed_up`% response rate) from England and Wales. 

# Methods

## Sample selection procedure

Figure 1, Section 4.2

```{r crossTabPlot, fig.cap="Counts of addresses contacted by region and IMD quintile", include = TRUE}

t <- table(results$region, results$quintile)
dt <- as.data.table(t)
setnames(dt, c("V1", "V2"), c("Region", "IMD"))
setkey(dt, Region)
dt[, imd_name := sapply(dt$IMD, function(x) {
  paste(x, " \n", dt[IMD == x, sum(N)], " total", sep = "")
})]
dt[, Region := sapply(dt$Region, function(x) {
  paste(x, " \n", dt[Region == x, sum(N)], " total", sep = "")
})]

imd_reg_tile <-
  ggplot2::ggplot(dt, aes(
    y = Region,
    x = imd_name,
    fill = N / 18000 * 100
  )) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "slateblue3") +
  geom_text(aes(label = paste(round(N / 18000 * 100, 1), "%", sep = "")),
            size = geom.text.size,
            family = myFont)  +
  labs(y = "Region",
       x = "IMD Quintile") +
  theme_light(base_family = myFont) +
  theme(text = element_text(size = font.size),
        axis.text.x = element_text(size = font.size - 1),
        axis.text.y = element_text(size = font.size - 1),
        legend.title = element_blank(),
        legend.text = element_text(size = font.size - 1),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.ticks = element_blank())

imd_reg_tile 

```

# Results

The pilot study recruited `r n_signups` participants; a `r perc_signed_up`% response rate (95% CI: `r signup_CI_low` - `r signup_CI_high`%).

`r n_survey_started` (`r perc_survey_started`%) participants completed or partially completed the (optional but encouraged) SERL survey;  `r perc_survey_completed`% of participants answered in full. 

`r n_survey_online` (`r round(n_survey_online / n_survey_started * 100, 1)`%) completed the survey online, `r n_survey_post` (`r round(n_survey_post / n_survey_started * 100, 1)`%) on paper and `r n_survey_both` (`r round(n_survey_both / n_survey_started * 100, 1)`%) did both. 


## Overall sample representativeness

```{r IMD}

start_imd <- results[, .N, keyby = quintile]
setnames(start_imd, "N", "StartingN")
consent_imd <- results[consent == TRUE, .N, keyby = quintile]
setnames(consent_imd, "N", "Participants")

descr_imd <- start_imd[consent_imd]
descr_imd[, ResponseRate := Participants / StartingN * 100]
descr_imd[, LowerCI := ResponseRate - 1.96 * 
            sqrt(ResponseRate * (100 - ResponseRate) / StartingN)]
descr_imd[, UpperCI := ResponseRate + 1.96 * 
            sqrt(ResponseRate * (100 - ResponseRate) / StartingN)]
setorder(descr_imd, -ResponseRate)

# Add final line to show overall results
all_stats <- data.table(quintile = "All", 
                        StartingN = results[, .N], 
                        Participants = results[consent == TRUE, .N])
all_stats[, ResponseRate := round(Participants / StartingN * 100, 1)]
all_stats[, LowerCI := round(ResponseRate - 1.96 * 
                               sqrt(ResponseRate * (100 - ResponseRate) / StartingN), 2)]
all_stats[, UpperCI := round(ResponseRate + 1.96 * 
                               sqrt(ResponseRate * (100 - ResponseRate) / StartingN), 2)]

descr_imd <- rbind(descr_imd, all_stats)
descr_imd <- format.percents(descr_imd)

out.imd <- my.flex(descr_imd)
out.imd <- set_header_labels(out.imd,
                             quintile = "IMD quintile",
                             StartingN = "Starting N",
                             ResponseRate = "Response Rate",
                             LowerCI = "Lower 95% CI",
                             UpperCI = "Upper 95% CI")

```

Table 3, Section 5.1.1

```{r, include = TRUE}
out.imd
```

```{r region}

start_reg <- results[, .N, keyby = region]
setnames(start_reg, "N", "StartingN")
consent_reg <- results[consent == TRUE, .N, keyby = region]
setnames(consent_reg, "N", "Participants")

descr_reg <- start_reg[consent_reg]
descr_reg[, ResponseRate := Participants / StartingN * 100]
descr_reg[, LowerCI := ResponseRate - 1.96 * 
            sqrt(ResponseRate * (100 - ResponseRate) / StartingN)]
descr_reg[, UpperCI := ResponseRate + 1.96 * 
            sqrt(ResponseRate * (100 - ResponseRate) / StartingN)]
setorder(descr_reg, -ResponseRate)

setnames(all_stats, "quintile", "region")
descr_reg <- rbind(descr_reg, all_stats)
descr_reg <- format.percents(descr_reg)

out.region <- my.flex(descr_reg)
out.region <- set_header_labels(out.region,
                             region = "Region",
                             StartingN = "Starting N",
                             ResponseRate = "Response Rate",
                             LowerCI = "Lower 95% CI",
                             UpperCI = "Upper 95% CI")

```

Table 4, Section 5.1.2

```{r, include = TRUE}
out.region
```


## Treatment effects

```{r logitModelNointeraction}

fullModelNoInteract <- glm(
  formula = consent ~ 
    factor(quintile, levels = c("3", "1", "2", "4", "5")) +
    factor(
      region,
      levels = c(
        "South East",
        "East Midlands",
        "East Of England",
        "Greater London",
        "South West",
        "Wales",
        "West Midlands"
      )
    ) +
    incentive +
    p2w +
    factor(version, levels = c("2", "1")),
  family = binomial(logit),
  results
) 

fullModelNoInteract2 <- broom::tidy(fullModelNoInteract)
fullModelNoInteract2 <- as.data.table(fullModelNoInteract2)
fullModelNoInteract2 <- cbind(list("Region"), fullModelNoInteract2)
setnames(fullModelNoInteract2, "V1", "Type")
fullModelNoInteract2[term == "(Intercept)", 
                     `:=`(Type = "Intercept", 
                          term = "")]
fullModelNoInteract2[str_detect(term, "quintile"), 
                     `:=`(Type = "IMD",
                          term = str_sub(term, -1, -1)
                          )]

# remove factor information
fullModelNoInteract2[str_detect(term, "region"),
   term := gsub(".*)","", term)]

fullModelNoInteract2[str_detect(term, "incentive"),
                     `:=`(Type = "Incentive",
                          term = sapply(fullModelNoInteract2[str_detect(term, "incentive"), 
                                                             term], 
                                        function(x) {
                                          str_sub(x, 10, str_length(x))
                                          })
                          )]
     
fullModelNoInteract2[term == "p2wTRUE", 
                     `:=`(Type = "Push to Web",
                          term = "TRUE")]

fullModelNoInteract2[str_detect(term, "version"),
   `:=`(Type = "Content version",
        term = "Version 1")]


fullModelNoInteract2[, oddsRatio := round(exp(estimate), 3)]

fullModelNoInteract3 <- cbind(fullModelNoInteract2, 
                              as.data.table(confint(fullModelNoInteract)))

fullModelNoInteract3[, ORlowerCI := exp(`2.5 %`)]
fullModelNoInteract3[, ORupperCI := exp(`97.5 %`)]
setcolorder(fullModelNoInteract3, c(1:3, 8:9, 7, 10:11, 4:6))
setnames(fullModelNoInteract3, 
         c("2.5 %", "97.5 %"), 
         c("CoeffLowerCI", "CoeffUpperCI"))

chosen_cols <- colnames(fullModelNoInteract3)[3:10]
for(i in chosen_cols) {
  fullModelNoInteract3[, eval(i) := round(get(i), 3)]
}

fullModelNoInteract3[, p.value := round(p.value, 3)]


# full output table
out.fullModelNoInteract <- my.flex(fullModelNoInteract3)
out.fullModelNoInteract <- set_header_labels(out.fullModelNoInteract,
                                             Type = "Category",
                                             term = "Variable",
                                             estimate = "Coefficient",
                                             CoeffLowerCI = "Coeff (lower 95%)",
                                             CoeffUpperCI = "Coeff (upper 95%)",
                                             oddsRatio = "Odds Ratio",
                                             ORlowerCI = "OR (lower 95%)",
                                             ORupperCI = "OR (upper 95%)",
                                             std.error = "Standard error",
                                             statistic = "Z value", 
                                             p.value = "P-value")

# treatment effects subtable
out.treatments <- my.flex(fullModelNoInteract3[Type %in% c("Incentive",
                                                           "Push to Web",
                                                           "Content version"), ])
out.treatments <- set_header_labels(
  out.treatments,
  Type = "Category",
  term = "Variable",
  estimate = "Coefficient",
  CoeffLowerCI = "Coeff (lower 95%)",
  CoeffUpperCI = "Coeff (upper 95%)",
  oddsRatio = "Odds Ratio",
  ORlowerCI = "OR (lower 95%)",
  ORupperCI = "OR (upper 95%)",
  std.error = "Standard error",
  statistic = "Z value",
  p.value = "P-value"
)

```

Table 5, Section 5.2
```{r, include = TRUE}
out.treatments

```


### Incentives

The conditional £5 voucher had a useful effect on sign-up to SERL, increasing participation from `r round(results[incentive == "None" & consent == TRUE, .N] / 6000 * 100, 1)`% (no incentive) to `r round(results[incentive == "Voucher" & consent == TRUE, .N] / 6000 * 100, 1)`%. 

### Push to web

This disadvantage of online sign up was that `r n_signups - n_survey_started` participants did not start the survey unlike all postal participants. 

```{r p2w}

# Create two tables: 1 with totals, one with percentages, merge manually

## Totals
p2w_n <- results[consent == TRUE, .N, keyby = p2w][c(2, 1)]
p2w_n[, Perc := round(N / 9000 * 100, 1)]

p2w_source <- results[consent == TRUE, .N, 
                      keyby = .(p2w, consent_source)][c(4, 6, 5, 1, 3, 2)]

p2w_n_tab <- data.table(Treatment = c("Push-to-web", "Control group"),
                    StartingN = rep(9000, 2),
                    Participants = p2w_n$N,
                    ResponseRate = p2w_n$Perc,
                    Online = p2w_source[consent_source == "online", N],
                    Post = p2w_source[consent_source == "postal", N],
                    Both = p2w_source[consent_source == "online+postal", N])

p2w_n_tab <- rbind(p2w_n_tab, 
                   c(list(Treatment = "All"), 
                     p2w_n_tab[, lapply(.SD, sum), .SDcols = 2:7]))

p2w_n_tab[Treatment == "All", ResponseRate := perc_signed_up]

p2w_n_tab_out <- my.flex(p2w_n_tab)

## Percentages
setkey(p2w_n, "p2w")
setkey(p2w_source, "p2w")
p2w_source <- p2w_n[p2w_source]
setnames(p2w_source, c("N", "i.N"), c("total", "N"))
p2w_source[, Perc_tot := round(N / total * 100, 1)]
p2w_source <- p2w_source[c(4:6, 1:3)]

p2w_p_tab <- data.table(Online = p2w_source[consent_source == "online", 
                                            Perc_tot],
                        Post = p2w_source[consent_source == "postal", 
                                          Perc_tot],
                        Both = p2w_source[consent_source == "online+postal", 
                                          Perc_tot])

p2w_p_tab <- rbind(p2w_p_tab, 
                   round(p2w_n_tab[3, 5:7] / n_signups * 100, 1))

p2w_p_tab_out <- my.flex(p2w_p_tab)

```


Table 6, Section 5.2.2
Totals
```{r, include = TRUE}
p2w_n_tab_out
```

Percentages to add to totals table
```{r, include = TRUE}
p2w_p_tab_out
```



### Message Content

```{r messageContent}

content <- results[consent == TRUE, .N, keyby = version]
content[, Perc := round(N / 9000 * 100, 1)]


content_tab <- data.table(Content = c("Treatment 1", "Treatment 2"),
                    StartingN = rep(9000, 2),
                    Participants = content$N,
                    ResponseRate = content$Perc)

content_tab_out <- my.flex(content_tab)

version1RespRate <- binom.test(
  results[consent == TRUE & version == "1", .N],
  results[version == "1", .N],
  p = results[consent == TRUE & version == "1", .N] / 9000,
  alternative = "two.sided",
  conf.level = 0.95
)

version2RespRate <- binom.test(
  results[consent == TRUE & version == "2", .N],
  results[version == "2", .N],
  p = 0.08877778,
  alternative = "two.sided",
  conf.level = 0.95
)
```

Table 7, Section 5.2.3
```{r, include = TRUE}
content_tab_out
```

Table 7 stats to add

Version 1 Response rate confidence intervals: `r version1RespRate$conf.int`

Version 2 Response rate confidence intervals: `r version2RespRate$conf.int`

Odds ratio and p-values come from the logit model in the Appendix. 


### Multiple reminders

```{r mailings}

mails <- results[consent == TRUE, .N, keyby = mailing]
mails[, StartingN := 18000]
for(i in 2:4) {
  mails[i, StartingN := mails[i-1, StartingN] - mails[i-1, N]]
}

mails[, Response := round(N / StartingN * 100, 1)]
mails[, PercOfSample := round(N/mails[, sum(N)]*100, 1)]

mails[, CumulResp := mails[1, N]]
for (i in 2:4) {
  mails[i, CumulResp := mails[i-1, CumulResp] + N]
  mails[i, PercIncrease := round(N / mails[i-1, CumulResp] * 100, 1)]
}

mails[, CumulResp := round(CumulResp / 18000 * 100, 1)]

mails_formatted <- mails[ ,c(1,3,2,4,6,5,7)]
format.percents(mails_formatted, 
                perc_cols = c("Response", 
                              "PercOfSample", 
                              "PercIncrease"))

mails_formatted[1, PercIncrease := ""]

out.mails <- my.flex(mails_formatted)

out.mails <- set_header_labels(
  out.mails,
  mailing = "Mailing",
  StartingN = "Starting N",
  N = "Participants per mailing",
  CumulResp = "Cumulative participants",
  Response = "Response rate per mailing",
  PercOfSample = "Percent of participants",
  PercIncrease = "% increase in participants"
)

my.imd.cols <- brewer.pal(9, "BuPu")[c(4, 6, 8, 9)]
p.imd.mails <- ggplot(results[consent == TRUE], 
                      aes(x = as.factor(quintile), 
                          fill = as.factor(mailing))) +
  geom_bar(position = position_stack(reverse = TRUE)) +
  theme_light(base_family = myFont)  +
    theme(legend.position = "bottom", 
          text = element_text(size = font.size - 6),
          panel.border = element_blank()) + 
  labs(fill = "Mailing", 
       x = "IMD quintile", 
       y = "Number of participants") + 
  scale_fill_manual(values = my.imd.cols) 

cumul_mailings <- results[mailing == 1]
cumul_mailings[, cumul_m := 1]
cumul_mailings <- rbind(cumul_mailings,
                        cbind(results[mailing %in% c(1, 2)],
                              data.table(cumul_m = rep(2, 
                                                       nrow(results[mailing %in% 
                                                                      c(1, 2)])
                                                       ))
                              ))

cumul_mailings <- rbind(cumul_mailings, 
                        cbind(results[mailing %in% c(1, 2, 3)],
                              data.table(cumul_m = rep(3, 
                                                       nrow(results[mailing %in% 
                                                                      c(1, 2, 3)])))
                                              ))

cumul_mailings <- rbind(cumul_mailings, 
                        cbind(results[mailing %in% c(1, 2, 3, 4)], 
                              data.table(cumul_m = rep(4, nrow(results[mailing %in% 
                                                                         c(1, 2, 3, 4)])))
                                              ))

my.imd.cols <- brewer.pal(9, "BuPu")[c(4, 5, 6, 8, 9)]
p.cumul.mail <- ggplot(cumul_mailings,
                       aes(x = cumul_m,
                           fill = factor(quintile))) + 
  geom_bar(position = "fill") +
  theme_light(base_family = myFont)  +
    theme(legend.position = "top",
          legend.box = "horizontal",
          text = element_text(size = font.size - 6),
          panel.border = element_blank()) + 
  labs(fill = "IMD quintile", 
       x = "Most recent mailing", 
       y = "% of participants in current sample") + 
  scale_fill_manual(values = my.imd.cols) + 
  scale_y_continuous(labels = scales::percent) + 
  guides(fill = guide_legend(title.position =  "top",
                             title.hjust = 0.5))

p.cumul.mail


```


Mailing 4 has the lowest response rate (`r mails[mailing == 4, round(Response, 1)]`%), increasing the total sample by around `r mails[mailing == 4, round(PercIncrease, 0)]`% (from `r mails[mailing == 3, CumulResp]`% to `r mails[mailing == 4, CumulResp]`%).


Table 8, Section 5.2.4

```{r, include = TRUE}
out.mails
```

Figure 2, Section 5.2.4

```{r fig.width = 3, fig.height = 4, include = TRUE}
p.cumul.mail

```


# Appendix

Table 9, Section 10.1
```{r, include = TRUE}
out.fullModelNoInteract

```

```{r logitModelInteractions}

interactionsModel <-
  glm(
    formula = consent ~ 
      factor(quintile, levels = c("3", "1", "2", "4", "5")) +
      factor(
        region,
        levels = c(
          "South East",
          "East Midlands",
          "East Of England",
          "Greater London",
          "South West",
          "Wales",
          "West Midlands")) +
      incentive +
      p2w +
      factor(version, levels = c("2", "1")) +
      incentive * factor(quintile, levels = c("3", "1", "2", "4", "5")) +
      p2w *  factor(quintile, levels = c("3", "1", "2", "4", "5")) , 
    family = binomial(logit), results
  )

summary(interactionsModel)

interactionsModel2 <-  broom::tidy(interactionsModel)
interactionsModel2 <- as.data.table(interactionsModel2)
interactionsModel2[, `:=`(p.value = round(p.value, 3),
                          estimate = round(estimate, 3),
                          std.error = round(std.error, 3),
                          statistic = round(statistic, 3))]
setnames(interactionsModel2, "term", "Var1")

interactionsModel2[Var1 == "(Intercept)", Var1 := "Intercept"]
interactionsModel2[str_detect(Var1, "region"),
   Var1 := gsub(".*)","", Var1)]

interactionsModel2[str_detect(Var1, "quintile"),
   Var1 := paste("IMD ", gsub(".*)","", Var1), sep = "")]

interactionsModel2[str_detect(Var1, "version"),
                   Var1 := paste("version ", gsub(".*)","", Var1), sep= "")]
                   
interactionsModel2[, Var1 := str_replace(Var1, "p2w", "Push to Web")]

interactionsModel2[, Var2 := gsub(".*:", "", Var1)]

interactionsModel2[Var1 == Var2, Var2 := NA]

interactionsModel2[, Var1 := gsub("\\:.*", "", Var1)]

interactionsModel2[, `:=`(Var1 = str_remove(Var1, "incentive"),
                          Var2 = str_remove(Var2, "incentive"))]

interactionsModel2[, `:=`(Var1 = str_remove(Var1, "TRUE"),
                          Var2 = str_remove(Var2, "TRUE"))]


interactionsModel2[, oddsRatio := round(exp(estimate), 3)]

interactionsModel2 <- cbind(interactionsModel2,
                              as.data.table(confint(interactionsModel)))

interactionsModel2[, ORlowerCI := exp(`2.5 %`)]
interactionsModel2[, ORupperCI := exp(`97.5 %`)]



setcolorder(interactionsModel2, c(1:3, 8:9, 7, 10:11, 4:6))
setnames(interactionsModel2, c("2.5 %", "97.5 %"), 
         c("CoeffLowerCI", "CoeffUpperCI"))

chosen_cols <- colnames(interactionsModel2)[4:8]
for(i in chosen_cols) {
  interactionsModel2[, eval(i) := round(get(i), 3)]
}

setcolorder(interactionsModel2, c("Var1", 
                                  "Var2", 
                                  "estimate",
                                  "CoeffLowerCI", 
                                  "CoeffUpperCI",
                                  "oddsRatio",
                                  "ORlowerCI",
                                  "ORupperCI",
                                  "std.error",
                                  "statistic",
                                  "p.value"))

setnames(interactionsModel2, c("Var1", "Var2"), c("Variable 1", "Variable 2"))

out.fullModelInteract <- my.flex(interactionsModel2)

out.fullModelInteract <- set_header_labels(
  out.fullModelInteract,
  Var1 = "Variable 1",
  Var2 = "Variable 2",
  estimate = "Coefficient",
  CoeffLowerCI = "Coeff (lower 95%)",
  CoeffUpperCI = "Coeff (upper 95%)",
  oddsRatio = "Odds Ratio",
  ORlowerCI = "OR (lower 95%)",
  ORupperCI = "OR (upper 95%)",
  std.error = "Standard error",
  statistic = "Z value",
  p.value = "P-value"
)



```



Table 10, Section 10.1

```{r, include = TRUE}
out.fullModelInteract

```



