---
title: "SERL pilot study paper analysis"
author: "Ellen Webborn"
date: 'Last run at: `r Sys.time()`'
output:
  word_document
---

```{r setup, include=FALSE}

library(data.table) 
library(ggplot2) 
library(broom) 
library(car) 
library(stringr)
library(flextable)
library(RColorBrewer)

# Set figure defaults
fig.h <- 5.5
fig.w <- 10
fullwidth <- TRUE
font.size <- 18
title.size <- 14
geom.text.size <- 7

knitr::opts_chunk$set(echo = FALSE, include = FALSE, message = FALSE, warning = FALSE, fig.width = fig.w, fig.height = fig.h, fig.fullwidth = fullwidth, dpi = 300)

options(scipen=999)

```


```{r functions}

# Format numbers with % in output tables
format.percents <-
  function(dt,
           perc_cols = c("ResponseRate", "LowerCI", "UpperCI"),
           decimals = 2) {
    for (j in perc_cols) {
      dt[, eval(j) := paste(format(round(get(j), digits = decimals), nsmall = decimals),
                            "%", sep = "")]
    }
    dt
  }

# Format output tables
my.flex <- function(t, autofit = FALSE) {
  ft <- flextable(t)
  ft <- theme_booktabs(ft)
  ft <- theme_zebra(ft, 
                    odd_header = rgb(84/255, 141/255, 212/255, 1),
                    even_body = "transparent",
                    odd_body = rgb(242/255, 242/255, 242/255, 1))
  ft <- color(ft, color = "white", part = "header")
  ft <- italic(ft, italic = TRUE, part = "header")
  ft <- bold(ft, bold = FALSE, part = "header")
  if(autofit == TRUE) {
    ft <- autofit(ft)
  } else{
    ft <- set_table_properties(ft, layout = "autofit")
  }
  return(ft)
}

```

```{r import}

# load data
load("N:/Documents/My publications/Pilot study paper/pilot_response_data_final.RData")

# import font
windowsFonts(`LM Roman 10` = windowsFont("LM Roman 10"))
myFont <- "LM Roman 10"

```

```{r basicStats}

n_signups <- results[consent == TRUE, .N]
perc_signed_up <- round(n_signups / 18000 * 100, 1)
n_survey_started <- results[survey_status %in% c("Completed", "Partially completed"), .N]
perc_survey_started <- round(n_survey_started / n_signups * 100, 1)
perc_survey_completed <- round(results[survey_status %in% c("Completed"), .N] / 
                                 n_signups * 100, 1)

n_survey_online <- results[survey_response_type == "online", .N]
n_survey_post <- results[survey_response_type == "postal", .N]
n_survey_both <- results[survey_response_type == "online + postal", .N]

# Results with confidence intervals
respRate <- binom.test(
  results[consent == TRUE, .N],
  18000,
  p = n_signups/18000,
  alternative = "two.sided",
  conf.level = 0.95
)
signup_CI_low <- round(respRate$conf.int[1] * 100, 1)
signup_CI_high <- round(respRate$conf.int[2] * 100, 1)


```



# Abstract

Up to 4 mailings were sent to 18,000 addresses, recruiting `r n_signups` participants (`r perc_signed_up`% response rate) from England and Wales. 


# Results

The pilot study recruited `r n_signups` participants; a `r perc_signed_up`% response rate (95% CI: `r signup_CI_low` - `r signup_CI_high`%).

`r n_survey_started` (`r perc_survey_started`%) participants completed or partially completed the (optional but encouraged) SERL survey;  `r perc_survey_completed`% of participants answered in full. 

`r n_survey_online` (`r round(n_survey_online / n_survey_started * 100, 1)`%) completed the survey online, `r n_survey_post` (`r round(n_survey_post / n_survey_started * 100, 1)`%) on paper and `r n_survey_both` (`r round(n_survey_both / n_survey_started * 100, 1)`%) did both. 


## Overall sample representativeness

```{r IMD}

start_imd <- results[, .N, keyby = quintile]
setnames(start_imd, "N", "StartingN")
consent_imd <- results[consent == TRUE, .N, keyby = quintile]
setnames(consent_imd, "N", "Participants")

descr_imd <- start_imd[consent_imd]
descr_imd[, ResponseRate := Participants / StartingN * 100]
descr_imd[, LowerCI := ResponseRate - 1.96 * 
            sqrt(ResponseRate * (100 - ResponseRate) / StartingN)]
descr_imd[, UpperCI := ResponseRate + 1.96 * 
            sqrt(ResponseRate * (100 - ResponseRate) / StartingN)]
setorder(descr_imd, -ResponseRate)

```


```{r region}

start_reg <- results[, .N, keyby = region]
setnames(start_reg, "N", "StartingN")
consent_reg <- results[consent == TRUE, .N, keyby = region]
setnames(consent_reg, "N", "Participants")

descr_reg <- start_reg[consent_reg]
descr_reg[, ResponseRate := Participants / StartingN * 100]
descr_reg[, LowerCI := ResponseRate - 1.96 * 
            sqrt(ResponseRate * (100 - ResponseRate) / StartingN)]
descr_reg[, UpperCI := ResponseRate + 1.96 * 
            sqrt(ResponseRate * (100 - ResponseRate) / StartingN)]
setorder(descr_reg, -ResponseRate)

```


## Treatment effects

```{r logitModelNointeraction}

fullModelNoInteract <- glm(
  formula = consent ~ 
    factor(quintile, levels = c("3", "1", "2", "4", "5")) +
    factor(
      region,
      levels = c(
        "South East",
        "East Midlands",
        "East Of England",
        "Greater London",
        "South West",
        "Wales",
        "West Midlands"
      )
    ) +
    incentive +
    p2w +
    factor(version, levels = c("2", "1")),
  family = binomial(logit),
  results
) 

fullModelNoInteract2 <- broom::tidy(fullModelNoInteract)
fullModelNoInteract2 <- as.data.table(fullModelNoInteract2)
fullModelNoInteract2 <- cbind(list("Region"), fullModelNoInteract2)
setnames(fullModelNoInteract2, "V1", "Type")
fullModelNoInteract2[term == "(Intercept)", 
                     `:=`(Type = "Intercept", 
                          term = "")]
fullModelNoInteract2[str_detect(term, "quintile"), 
                     `:=`(Type = "IMD",
                          term = str_sub(term, -1, -1)
                          )]

# remove factor information
fullModelNoInteract2[str_detect(term, "region"),
   term := gsub(".*)","", term)]

fullModelNoInteract2[str_detect(term, "incentive"),
                     `:=`(Type = "Incentive",
                          term = sapply(fullModelNoInteract2[str_detect(term,
                                                                        "incentive"),
                                                             term], 
                                        function(x) {
                                          str_sub(x, 10, str_length(x))
                                          })
                          )]
     
fullModelNoInteract2[term == "p2wTRUE", 
                     `:=`(Type = "Push to Web",
                          term = "TRUE")]

fullModelNoInteract2[str_detect(term, "version"),
   `:=`(Type = "Content Version",
        term = "Version 1")]


fullModelNoInteract2[, oddsRatio := round(exp(estimate), 3)]

fullModelNoInteract3 <- cbind(fullModelNoInteract2, 
                              as.data.table(confint(fullModelNoInteract)))

fullModelNoInteract3[, ORlowerCI := exp(`2.5 %`)]
fullModelNoInteract3[, ORupperCI := exp(`97.5 %`)]

# Get sample sizes 
imd_n <- results[quintile != 3, .N, keyby = quintile]
reg_n <- results[region != "South East", .N, keyby = region]

fullModelNoInteract3[, N := c(18000,
                              imd_n$N,
                              reg_n$N,
                              6000, 6000,
                              9000, 9000)]



setcolorder(fullModelNoInteract3, c(1,2, 12, 3, 8:9, 7, 10:11, 4:6))
setnames(fullModelNoInteract3, 
         c("2.5 %", "97.5 %"), 
         c("CoeffLowerCI", "CoeffUpperCI"))

chosen_cols <- colnames(fullModelNoInteract3)[4:12]
for(i in chosen_cols) {
  fullModelNoInteract3[, eval(i) := round(get(i), 3)]
}


# full output table
out.fullModelNoInteract <- my.flex(fullModelNoInteract3)
out.fullModelNoInteract <- set_header_labels(out.fullModelNoInteract,
                                             Type = "Category",
                                             term = "Variable",
                                             estimate = "Coefficient",
                                             CoeffLowerCI = "Coeff (lower 95%)",
                                             CoeffUpperCI = "Coeff (upper 95%)",
                                             oddsRatio = "Odds Ratio",
                                             ORlowerCI = "OR (lower 95%)",
                                             ORupperCI = "OR (upper 95%)",
                                             std.error = "Standard error",
                                             statistic = "Z value", 
                                             p.value = "P-value")

# treatment effects subtable
treat_results <- fullModelNoInteract3[Type %in% c("Incentive",
                                                  "Push to Web",
                                                  "Content Version"),
                                      .(Type, 
                                        term,
                                        estimate,
                                        CoeffLowerCI,
                                        CoeffUpperCI,
                                        oddsRatio,
                                        ORlowerCI,
                                        ORupperCI,
                                        p.value)]

treat_results2 <- rbind(data.table(Type = "Incentive", 
                                   term = "None"),
                       treat_results[1:2],
                       data.table(Type = "Push to Web", 
                                   term = "FALSE"),
                       treat_results[3:4],
                       data.table(Type = "Content Version", 
                                   term = "Version 2"),
                       fill = TRUE)

treat_results2[, StartingN := c(rep(6000, 3), 
                                rep(9000, 4))]

treat_results2[, Participants := sapply(1:nrow(treat_results2), function(x) {
  if(treat_results2[x, Type == "Incentive"] == TRUE) {
    y <- results[consent == TRUE & incentive == treat_results2[x, term], .N]
  } else if(treat_results2[x, Type == "Push to Web"] == TRUE) {
    y <- results[consent == TRUE & p2w == treat_results2[x, term], .N]
  } else {
    y <- results[consent == TRUE & version == substring(treat_results2[x, term], 9), .N]
  }
  return(y)
  })]

treat_results2[, PercResp := round(Participants / StartingN * 100, 1)]
treat_results2[, lowCIrespRate := round(PercResp - 1.96 * sqrt(PercResp * (100 - PercResp) / StartingN),
                                        1)]
treat_results2[, highCIrespRate := round(PercResp + 1.96 * sqrt(PercResp * (100 - PercResp) / StartingN),
                                        1)]

treat_results2[Type == "Incentive", PercPtChange := round(PercResp - 
                                                            treat_results2[term == "None",
                                                                           PercResp], 
                                                          1)]
treat_results2[term == "TRUE", PercPtChange := round(PercResp -
                                                       treat_results2[term == "FALSE",
                                                                      PercResp], 
                                                          1)]
treat_results2[term == "Version 1", PercPtChange := round(PercResp - 
                                                            treat_results2[term == "Version 2",
                                                                           PercResp], 
                                                          1)]

out.treatments <- my.flex(treat_results2[, .(Type, term, StartingN, Participants, PercResp,
                                             lowCIrespRate, highCIrespRate,PercPtChange,
                                             oddsRatio, ORlowerCI, ORupperCI, p.value)])

out.treatments <- set_header_labels(
  out.treatments,
  Type = "Category",
  term = "Variable",
  oddsRatio = "Odds Ratio",
  ORlowerCI = "OR (lower 95%)",
  ORupperCI = "OR (upper 95%)",
  p.value = "P-value",
  percResp = "Response rate"
)

```

Table 3, Section 5
```{r, include = TRUE}
out.treatments
```


### Incentives

The conditional £5 voucher had a useful effect on sign-up to SERL, increasing participation from `r round(results[incentive == "None" & consent == TRUE, .N] / 6000 * 100, 1)`% (no incentive) to `r round(results[incentive == "Voucher" & consent == TRUE, .N] / 6000 * 100, 1)`%. 

```{r incentivebars}

txt_size_bar <- 4.5
txt_size_err_bar <- 4
txt_size_axis_label <- 4
low_ci_vjust <- 2.8
high_ci_vjust <- -2
main_vjust <- 10

theme_set(theme_light(base_family = myFont))
update_geom_defaults("text", list(family = theme_get()$text$family))

inc_bar <- ggplot(treat_results2[Type == "Incentive"],
                  aes(x = term, y = PercResp)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = lowCIrespRate,
                    ymax = highCIrespRate),
                width = 0.5) +
  coord_cartesian(ylim = c(0, 12)) + 
  geom_text(aes(label = paste(PercResp, "%", sep = "")),
            vjust = main_vjust, color = "white",
            size = txt_size_bar) + 
  geom_text(aes(label = paste(lowCIrespRate, "%", sep = "")),
            vjust = low_ci_vjust, color = "white",
            size = txt_size_err_bar) +
  geom_text(aes(label = paste(highCIrespRate, "%", sep = "")),
            vjust = high_ci_vjust, color = "black",
            size = txt_size_err_bar) +
  labs(x = "Incentive treatment", 
       y = "Response rate (%)") + 
  theme(text = element_text(size = font.size - 6),
          panel.border = element_blank())

```


Figure 1, Section 5.1

```{r fig.width = 3, fig.height = 3.5, include = TRUE}
inc_bar
```

### Push to web

This disadvantage of online sign up was that `r n_signups - n_survey_started` participants did not start the survey unlike all postal participants. 

```{r p2w}

# Create two tables: 1 with totals, one with percentages, merge manually

## Totals
p2w_n <- results[consent == TRUE, .N, keyby = p2w][c(2, 1)]
p2w_n[, Perc := round(N / 9000 * 100, 1)]

p2w_source <- results[consent == TRUE, .N, 
                      keyby = .(p2w, consent_source)][c(4, 6, 5, 1, 3, 2)]

p2w_n_tab <- data.table(Treatment = c("Push-to-web", "Control group"),
                    StartingN = rep(9000, 2),
                    Participants = p2w_n$N,
                    ResponseRate = p2w_n$Perc,
                    Online = p2w_source[consent_source == "online", N],
                    Post = p2w_source[consent_source == "postal", N],
                    Both = p2w_source[consent_source == "online+postal", N])

p2w_n_tab <- rbind(p2w_n_tab, 
                   c(list(Treatment = "All"), 
                     p2w_n_tab[, lapply(.SD, sum), .SDcols = 2:7]))

p2w_n_tab[Treatment == "All", ResponseRate := perc_signed_up]


## Percentages
setkey(p2w_n, "p2w")
setkey(p2w_source, "p2w")
p2w_source <- p2w_n[p2w_source]
setnames(p2w_source, c("N", "i.N"), c("total", "N"))
p2w_source[, Perc_tot := round(N / total * 100, 1)]
p2w_source <- p2w_source[c(4:6, 1:3)]

p2w_p_tab <- data.table(Online = p2w_source[consent_source == "online", 
                                            Perc_tot],
                        Post = p2w_source[consent_source == "postal", 
                                          Perc_tot],
                        Both = p2w_source[consent_source == "online+postal", 
                                          Perc_tot])

p2w_p_tab <- rbind(p2w_p_tab, 
                   round(p2w_n_tab[3, 5:7] / n_signups * 100, 1))

p2w_p_tab_out <- my.flex(p2w_p_tab)


# standard bar chart

p2w_bar <- ggplot(treat_results2[Type == "Push to Web"],
                  aes(x = term, y = PercResp)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = lowCIrespRate,
                    ymax = highCIrespRate),
                width = 0.5) +
  coord_cartesian(ylim = c(0, 12)) + 
  geom_text(aes(label = paste(format(PercResp, nsmall = 1), "%", sep = "")),
            vjust = main_vjust, color = "white",
            size = txt_size_bar) + 
  geom_text(aes(label = paste(lowCIrespRate, "%", sep = "")),
            vjust = low_ci_vjust, color = "white",
            size = txt_size_err_bar) +
  geom_text(aes(label = paste(highCIrespRate, "%", sep = "")),
            vjust = high_ci_vjust, color = "black",
            size = txt_size_err_bar) +
  labs(x = "Push to Web treatment", 
       y = "Response rate (%)") + 
  theme(text = element_text(size = font.size - 6),
          panel.border = element_blank())

# bar chart with response method

p2w_n_tab[, term := as.character((Treatment == "Push-to-web"))]
setkey(p2w_n_tab, "term")
p2w_n_tab <- p2w_n_tab[Treatment != "All"]
setkey(treat_results2, "term")

p2w_results <- p2w_n_tab[, .(term, Online, Post, Both)][treat_results2[Type == "Push to Web"]]

p2w_results2 <- melt(p2w_results, measure.vars = c("Online", "Post", "Both"), value.name = "N_by_method")

p2w_results2[, perc_by_method := N_by_method / StartingN * 100]
p2w_results2[, perc_of_method := round(N_by_method / Participants * 100, 1)]


p2w_bar2 <- ggplot(p2w_results2,
                  aes(x = term, y = perc_by_method, fill = variable)) + 
  geom_bar(stat = "identity") + 
  coord_cartesian(ylim = c(0, 12)) + 
  labs(x = "Push-to-web treatment", 
       y = "Response rate (%)") + 
  theme(text = element_text(size = font.size - 6),
        legend.position = "top",
        legend.box = "horizontal",
        panel.border = element_blank()) + 
  guides(fill = guide_legend(title = "Response method", 
                             title.position =  "top",
                             title.hjust = 0.5)) + 
  annotate(geom = "text", x = 1, y = 8, label = "35.3%", color = "white") + 
  annotate(geom = "text", x = 1, y = 3, label = "62.4%") + 
  annotate(geom = "text", x = 1, y = 0.2, label = "2.3%") +
  annotate(geom = "text", x = 2, y = 6, label = "64.3%", color = "white") + 
  annotate(geom = "text", x = 2, y = 1.5, label = "31.6%") + 
  annotate(geom = "text", x = 2, y = 0.2, label = "4.1%") + 
  scale_fill_brewer(palette = "Greys", direction = -1)



p2w_bar2
```

Figure 2, Section 5.2
```{r fig.width = 3, fig.height = 3.5, include = TRUE}
p2w_bar

```

Figure 3, Section 5.2
```{r fig.width = 3, fig.height = 3.5*33.8/28, include = TRUE}
p2w_bar2

```


### Message Content

```{r messageContent}

content_bar <- ggplot(treat_results2[Type == "Content Version"],
                  aes(x = term, y = PercResp)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = lowCIrespRate,
                    ymax = highCIrespRate),
                width = 0.5) +
  coord_cartesian(ylim = c(0, 12)) + 
  geom_text(aes(label = paste(PercResp, "%", sep = "")),
            vjust = main_vjust, color = "white",
            size = txt_size_bar) + 
  geom_text(aes(label = paste(lowCIrespRate, "%", sep = "")),
            vjust = low_ci_vjust, color = "white",
            size = txt_size_err_bar) +
  geom_text(aes(label = paste(highCIrespRate, "%", sep = "")),
            vjust = high_ci_vjust, color = "black",
            size = txt_size_err_bar) +
  labs(x = "Content Version", 
       y = "Response rate (%)") + 
  theme(text = element_text(size = font.size - 6),
          panel.border = element_blank())

```

Figure 4, Section 5.3
```{r fig.width = 3, fig.height = 3.5, include = TRUE}
content_bar

```



### Multiple reminders

```{r mailings}

mails <- results[consent == TRUE, .N, keyby = mailing]
mails[1, StartingN := 18000]
mails[1, TotalN := N]
for(i in 2:4) {
  mails[i, StartingN := mails[i-1, StartingN] - mails[i-1, N]]
  mails[i, TotalN := mails[i-1, TotalN + mails[i, N]]]
}

mails[, `:=`(OverallRespRate = round(TotalN / 18000 * 100, 1),
             MailingRespRate = round(N / StartingN * 100, 1))]

for (i in 2:4) {
  mails[i, pctPtInc := OverallRespRate - mails[i-1, OverallRespRate]]
  mails[i, pctInc := round((OverallRespRate - mails[i-1, OverallRespRate]) / 
                             mails[i-1, OverallRespRate] * 100, 1)]
}

setcolorder(mails, c("mailing",
                     "StartingN",
                     "N",
                     "MailingRespRate",
                     "TotalN",
                     "OverallRespRate",
                     "pctPtInc",
                     "pctInc"))

formatted_mails <- format.percents(
  mails,
  perc_cols = c("MailingRespRate",
                "OverallRespRate",
                "pctPtInc",
                "pctInc"),
  decimals = 1
)

formatted_mails[1, `:=`(pctPtInc = "", pctInc = "")]

out.mails <- my.flex(formatted_mails)

out.mails <- set_header_labels(
  out.mails,
  mailing = "Mailing",
  StartingN = "Starting N",
  N = "Participants",
  MailingRespRate = "Mailing response rate",
  TotalN = "Total Participants",
  OverallRespRate = "Overall response rate",
  pctPtInc = "% point increase in participants",
  pctInc = "% increase in participants"
)

```


Table 4, Section 5.4

```{r, include = TRUE}
out.mails
```


### Treatment effects on response outcome by IMD and region

Households in areas with greatest deprivation were least likely to respond (`r descr_imd[quintile == 1, round(ResponseRate, 1)]`% response from IMD quintile 1) compared with `r descr_imd[quintile == 5, round(ResponseRate, 1)]`% response from IMD quintile 5 (the most affluent areas). Regionally, response rates ranged from `r descr_reg[region == "East Midlands", round(ResponseRate, 1)]`% (East Midlands) to `r descr_reg[region == "Wales", round(ResponseRate, 1)]`% (Wales).


# Appendix

Table 5, Section 10.1
```{r, include = TRUE}
out.fullModelNoInteract

```

```{r logitModelInteractionsIMD}

results2 <- copy(results)
results2[, version := factor(version, levels = c("2", "1"))]

interactionsModel <-
  glm(
    formula = consent ~ 
      factor(quintile, levels = c("3", "1", "2", "4", "5")) +
      factor(
        region,
        levels = c(
          "South East",
          "East Midlands",
          "East Of England",
          "Greater London",
          "South West",
          "Wales",
          "West Midlands")) +
      incentive +
      p2w +
      version +
      incentive * factor(quintile, levels = c("3", "1", "2", "4", "5")) +
      p2w *  factor(quintile, levels = c("3", "1", "2", "4", "5")) +
      version * factor(quintile, levels = c("3", "1", "2", "4", "5")),
    family = binomial(logit), results2
  )

summary(interactionsModel)

interactionsModel2 <-  broom::tidy(interactionsModel)
interactionsModel2 <- as.data.table(interactionsModel2)
interactionsModel2[, `:=`(p.value = round(p.value, 3),
                          estimate = round(estimate, 3),
                          std.error = round(std.error, 3),
                          statistic = round(statistic, 3))]
setnames(interactionsModel2, "term", "Var1")

interactionsModel2[Var1 == "(Intercept)", Var1 := "Intercept"]
interactionsModel2[str_detect(Var1, "region"),
   Var1 := gsub(".*)","", Var1)]

interactionsModel2[str_detect(Var1, "quintile"),
   Var1 := paste("IMD ", gsub(".*)","", Var1), sep = "")]

interactionsModel2[str_detect(Var1, "version"),
                   Var1 := paste("version ", gsub(".*)","", Var1), sep= "")]
                   
interactionsModel2[, Var1 := str_replace(Var1, "p2w", "Push to Web")]

interactionsModel2[, Var2 := gsub(".*:", "", Var1)]

interactionsModel2[Var1 == Var2, Var2 := NA]

interactionsModel2[, Var1 := gsub("\\:.*", "", Var1)]

interactionsModel2[, `:=`(Var1 = str_remove(Var1, "incentive"),
                          Var2 = str_remove(Var2, "incentive"))]

interactionsModel2[, `:=`(Var1 = str_remove(Var1, "TRUE"),
                          Var2 = str_remove(Var2, "TRUE"))]

interactionsModel2[, `:=`(Var1 = str_remove(Var1, "version "),
                          Var2 = str_replace(Var2, "version", "Version "))]

interactionsModel2[, `:=`(Var1 = str_replace(Var1, "version", "Version "))]

interactionsModel2[, oddsRatio := round(exp(estimate), 3)]

interactionsModel2 <- cbind(interactionsModel2,
                              as.data.table(confint(interactionsModel)))

interactionsModel2[, ORlowerCI := exp(`2.5 %`)]
interactionsModel2[, ORupperCI := exp(`97.5 %`)]

# Get sample sizes
imd_inc_n <- results[quintile != 3 & incentive != "None", .N, 
                 keyby = .(incentive, quintile)]

imd_p2w_n <- results[quintile != 3 & p2w == TRUE, .N, 
                 keyby = .(quintile)]

imd_version_n <- results[quintile != 3 & version == 1, .N, 
                 keyby = .(quintile)]


interactionsModel2[, N := c(18000,
                            imd_n$N,
                            reg_n$N,
                            6000, 6000,
                            9000, 9000,
                            imd_inc_n$N,
                            imd_p2w_n$N,
                            imd_version_n$N)]


setcolorder(interactionsModel2, c(1, 2, 12, 3, 8:9, 7, 10:11, 4:6))
setnames(interactionsModel2, c("2.5 %", "97.5 %"), 
         c("CoeffLowerCI", "CoeffUpperCI"))

chosen_cols <- colnames(interactionsModel2)[5:9]
for(i in chosen_cols) {
  interactionsModel2[, eval(i) := round(get(i), 3)]
}


setcolorder(interactionsModel2, c("Var1", 
                                  "Var2", 
                                  "N", 
                                  "estimate",
                                  "CoeffLowerCI", 
                                  "CoeffUpperCI",
                                  "oddsRatio",
                                  "ORlowerCI",
                                  "ORupperCI",
                                  "std.error",
                                  "statistic",
                                  "p.value"))

setnames(interactionsModel2, c("Var1", "Var2"), c("Variable 1", "Variable 2"))

out.fullModelInteract <- my.flex(interactionsModel2)

out.fullModelInteract <- set_header_labels(
  out.fullModelInteract,
  Var1 = "Variable 1",
  Var2 = "Variable 2",
  estimate = "Coefficient",
  CoeffLowerCI = "Coeff (lower 95%)",
  CoeffUpperCI = "Coeff (upper 95%)",
  oddsRatio = "Odds Ratio",
  ORlowerCI = "OR (lower 95%)",
  ORupperCI = "OR (upper 95%)",
  std.error = "Standard error",
  statistic = "Z value",
  p.value = "P-value"
)



```



Table 6, Section 10.1
Interacting treatments with IMD quintile
```{r, include = TRUE}
out.fullModelInteract

```


```{r logitModelInteractionsRegion}

interactionsModelR <-
  glm(
    formula = consent ~ 
      factor(quintile, levels = c("3", "1", "2", "4", "5")) +
      factor(
        region,
        levels = c(
          "South East",
          "East Midlands",
          "East Of England",
          "Greater London",
          "South West",
          "Wales",
          "West Midlands")) +
      incentive +
      p2w +
      version +
      incentive * factor(
        region,
        levels = c(
          "South East",
          "East Midlands",
          "East Of England",
          "Greater London",
          "South West",
          "Wales",
          "West Midlands")) +
      p2w * factor(
        region,
        levels = c(
          "South East",
          "East Midlands",
          "East Of England",
          "Greater London",
          "South West",
          "Wales",
          "West Midlands")) + 
      version * factor(
        region,
        levels = c(
          "South East",
          "East Midlands",
          "East Of England",
          "Greater London",
          "South West",
          "Wales",
          "West Midlands")),
    family = binomial(logit), results2
  )

summary(interactionsModelR)

interactionsModelR2 <-  broom::tidy(interactionsModelR)
interactionsModelR2 <- as.data.table(interactionsModelR2)
interactionsModelR2[, `:=`(p.value = round(p.value, 3),
                          estimate = round(estimate, 3),
                          std.error = round(std.error, 3),
                          statistic = round(statistic, 3))]
setnames(interactionsModelR2, "term", "Var1")

interactionsModelR2[Var1 == "(Intercept)", Var1 := "Intercept"]
interactionsModelR2[str_detect(Var1, "region"),
   Var1 := gsub(".*)","", Var1)]

interactionsModelR2[str_detect(Var1, "quintile"),
   Var1 := paste("IMD ", gsub(".*)","", Var1), sep = "")]

interactionsModelR2[str_detect(Var1, "version"),
                   Var1 := paste("version ", gsub(".*)","", Var1), sep= "")]
                   
interactionsModelR2[, Var1 := str_replace(Var1, "p2w", "Push to Web")]

interactionsModelR2[, Var2 := gsub(".*:", "", Var1)]

interactionsModelR2[Var1 == Var2, Var2 := NA]

interactionsModelR2[, Var1 := gsub("\\:.*", "", Var1)]

interactionsModelR2[, `:=`(Var1 = str_remove(Var1, "incentive"),
                          Var2 = str_remove(Var2, "incentive"))]

interactionsModelR2[, `:=`(Var1 = str_remove(Var1, "TRUE"),
                          Var2 = str_remove(Var2, "TRUE"))]

interactionsModelR2[, `:=`(Var1 = str_remove(Var1, "version "),
                          Var2 = str_replace(Var2, "version", "Version "))]

interactionsModelR2[, oddsRatio := round(exp(estimate), 3)]

interactionsModelR2 <- cbind(interactionsModelR2,
                              as.data.table(confint(interactionsModelR)))

interactionsModelR2[, ORlowerCI := exp(`2.5 %`)]
interactionsModelR2[, ORupperCI := exp(`97.5 %`)]



# Get sample sizes
reg_inc_n <- results[region != "South East" & incentive != "None", .N, 
                 keyby = .(incentive, region)]

reg_p2w_n <- results[region != "South East" & p2w == TRUE, .N, 
                 keyby = .(region)]

reg_version_n <- results[region != "South East" & version == 1, .N, 
                 keyby = .(region)]


interactionsModelR2[, N := c(18000,
                            imd_n$N,
                            reg_n$N,
                            6000, 6000,
                            9000, 9000,
                            reg_inc_n$N,
                            reg_p2w_n$N,
                            reg_version_n$N)]


setcolorder(interactionsModelR2, c(1, 2, 12, 3, 8:9, 7, 10:11, 4:6))

setnames(interactionsModelR2, c("2.5 %", "97.5 %"), 
         c("CoeffLowerCI", "CoeffUpperCI"))

chosen_cols <- colnames(interactionsModelR2)[5:9]
for(i in chosen_cols) {
  interactionsModelR2[, eval(i) := round(get(i), 3)]
}

#interactionsModelR12[1:5, N :=]

setcolorder(interactionsModelR2, c("Var1", 
                                  "Var2", 
                                  "N",
                                  "estimate",
                                  "CoeffLowerCI", 
                                  "CoeffUpperCI",
                                  "oddsRatio",
                                  "ORlowerCI",
                                  "ORupperCI",
                                  "std.error",
                                  "statistic",
                                  "p.value"))

setnames(interactionsModelR2, c("Var1", "Var2"), c("Variable 1", "Variable 2"))

out.fullModelInteractR <- my.flex(interactionsModelR2)

out.fullModelInteractR <- set_header_labels(
  out.fullModelInteractR,
  Var1 = "Variable 1",
  Var2 = "Variable 2",
  estimate = "Coefficient",
  CoeffLowerCI = "Coeff (lower 95%)",
  CoeffUpperCI = "Coeff (upper 95%)",
  oddsRatio = "Odds Ratio",
  ORlowerCI = "OR (lower 95%)",
  ORupperCI = "OR (upper 95%)",
  std.error = "Standard error",
  statistic = "Z value",
  p.value = "P-value"
)



```


Table 7, Section 10.1
Interacting treatments with region

```{r, include = TRUE}
out.fullModelInteractR

```